---
title: "Activity Analysis"
author: "Emmet Murphy"
date: "June 6, 2016"
output: html_document
---
```{r, hide=TRUE}
library(ggplot2)
```

### Load the data

1. Read in the CSV.

```{r}
activities <- read.csv(unz('activity.zip', 'activity.csv'))
```

### What is mean total number of steps taken per day?

1. Calculate total number of steps per day.

```{r}
steps_per_day <- aggregate(activities$steps, by=list(activities$date), sum)
```

2. Plot a histogram of the total number of steps per day.

```{r}
names(steps_per_day) = c("date", "steps") 
hist(steps_per_day$steps)
```

3. Summarize the total number of steps per day, including mean and median.

```{r}
summary(steps_per_day)
```

### What is the average daily activity pattern?

1. Time series plot the average number of steps taken per 5-minute interval, averaged across all days.

```{r}
avg_steps_per_interval <- aggregate(activities$steps, by=list(activities$interval), mean, na.rm=TRUE)
names(avg_steps_per_interval) = c("interval", "steps") 
g <- ggplot(avg_steps_per_interval, aes(interval, steps))
g + geom_line()
```

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
avg_steps_per_interval[which.max(avg_steps_per_interval$steps),]
```
